---
title: "Exercise-11-git-markdown"
author: "MM"
date: "2024-12-20"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Downloading packages :

```{r, eval=TRUE, results = "hide", echo=TRUE}
library(dplyr)
library(tidyverse)
library(broom)
library(haven)
x<-read_sav("data/ESS9e03_2.sav")
```



# Having a look at the dataset :
```{r, eval=TRUE, echo=TRUE}
head(x)
```


# Data preparation
### Finding the variables in the documentation :
- age -> agea</br>
- sex -> gndr -> to recode : 1 female; 0 male </br>
- employment relationship -> emplrel</br>
- marital status -> marsts -> to be recoded into 3 groups</br>
- subjective income -> hincfel</br>
- religious attendance -> rlgatnd _> recode</br>

### Selecting the variables we need and creating a dataset :
```{r, eval=TRUE, results = "hide", echo=TRUE}
df<-select(x,
           age = agea,
           sex = gndr,
           emplrel,
           marsts,
           subjinc = hincfel,
           rlgatnd,
           cntry
           )
```
### Quickly exploring the variables in question :
```{r, eval=TRUE, echo=TRUE}
table(as_factor(df$sex))
table(df$sex)
```
Since female is coded as 2, and male as 1 we can just substract 1
```{r, eval=TRUE, results = "hide", echo=TRUE}
df<-mutate(df, sex=sex-1)
```
```{r, eval=TRUE, echo=TRUE}
table(df$sex)
table(df$emplrel)
df.emplrel<-as.factor(df$emplrel)
table(as_factor(df$marsts))
table(df$marsts)
```
### Recoding marital status :
#### 1or2;3or4or5;6or66or77or88or99</br>
Eventually this code will transform NA into 3rd category</br>
There haven't been restrictions about that so we keep it !
```{r, eval=TRUE, results = "hide", echo=TRUE}
df<-mutate(df,marsts=ifelse(marsts %in% c(1,2),1,
                            ifelse(marsts %in% c(3,4,5),2,3)))
table(df$marsts)
```
### Recoding religion attendance :
```{r, eval=TRUE, results = "hide", echo=FALSE}
table(as_factor(df$rlgatnd))
table(df$rlgatnd)
```
```{r, eval=TRUE, echo=TRUE}
df<-mutate(df,rlgatnd = 7-rlgatnd)
table(df$rlgatnd)
```
# [QUESTION 2.1] 
## Report the percentage of females in the sample : 53.51%.
```{r, eval=TRUE, results = "hide", echo=TRUE}
female<-round(nrow(filter(df,sex==1))/nrow(df),4)*100
```
```{r, eval=TRUE, echo=FALSE}
female
```
# [QUESTION 2.2] 
## Report the percentage of separated, divorced or widowed individuals in the sample, after recoding marital status : 19.36%.
```{r, eval=TRUE, results = "hide", echo=TRUE}
prop.table(table(df$marsts))
nonmarried<-round(nrow(filter(df,marsts==2))/nrow(df),4)*100
```
```{r, eval=TRUE, echo=FALSE}
nonmarried
```
# [QUESTION 2.3] 
## Report average religious attendance in the sample, after recoding it, and treating it as a continuous measurement : 1.53%.
```{r, eval=TRUE, results = "hide", echo=TRUE}
avg_rlgatnd<-round(mean(df$rlgatnd,na.rm=TRUE),2)
```
```{r, eval=TRUE, echo=FALSE}
avg_rlgatnd
```
# 3. Write a multiple linear regression model :

Including an interaction term :
```{r, eval=TRUE, results="hide", echo=TRUE}
df<-mutate(df,sexmar=df$sex*df$marsts)
```
# [QUESTION 3] 
## Provide the formula of your model, in R syntax :
```{r, eval=TRUE, echo=TRUE}
m1<-lm(rlgatnd~age+sex+emplrel+marsts+subjinc+sexmar,data=df)
```
# 4. Interpret regression results :
## Straightforward model summary :
```{r, eval=TRUE, echo=TRUE}
summary(m1)
```
## Fancy model output :
```{r, eval=TRUE, echo=TRUE}
texreg::screenreg(m1)
```
All coefficients are statistically significant both under p<0.001 and p<0.05. However, both R-squared and adjusted R-squared are super low. Hence, the model has a low predictive ability.

# [QUESTION 4.1] 

## Do females report higher religious attendance than males,independently of age, employment status, marital status or subjective income? (Answer Yes or No.)

## Yes
This is what the positive coefficient of <b>sex</b> variable indicates. 

# [QUESTION 4.2] 

## Does the model support the view that economic insecurity increases religious attendance?

## Yes
The coefficient for income self-assessment is positive thus the more insecure respondents are, the more religious they are. Same for employment. Employed are less religious than those who work independently.

# [QUESTION 4.3]

## How do you interpret the interaction in the model?

Interaction coefficient in general : 0 for men. So it is controlling for women measuring how women marriage status affect their religiousness. Basically, since its negative the less married the women is the less she will be religious. Whereas if she lives or has lived with a man, she tends to be more religious.

# 5. Diagnose a linear regression model

Firstly, it is worth mentioning that the adjusted R-squared is super low which means that only 4% of variation in religiousness is explained by the predictors.

# [QUESTION 5] 

## According to its residuals, how biased is the model, and what does that mean in terms of its capacity to predict religious attendance from our list of predictors?

```{r, eval=TRUE, echo=TRUE}
m1_aug<-augment(m1)
p <- ggplot(data = m1_aug,
            mapping = aes(x = .fitted, y = .resid))
p + geom_point()
```
</br>

The residuals vs fitted plot indicates that the model is super biased residuals are not randomly distributed around 0 and higher residuals are associated with lower fitted values.

# 6. Start thinking beyond 'flat' models
# [QUESTION 6.1] 
## Report the country-level effect for Poland. 1.4 (Answer with a single number, rounded up to 1-digit precision.)

First, lets have a look at countries
```{r, eval=TRUE, echo=TRUE}
df$cntry<-as.factor(df$cntry)
table(as_factor(df$cntry))
```
Let's run the model with a country
```{r, eval=TRUE, echo=TRUE}
m2<-lm(rlgatnd~age+sex+emplrel+marsts+subjinc+sexmar+cntry,data=df)
```
```{r, eval=TRUE, echo=FALSE}
texreg::screenreg(m2)
```
What is the country level effect for Poland ?
```{r, eval=TRUE, echo=TRUE}
round(coef(m2)["cntryPL"],1)
```
# [QUESTION 6.2] 
## Can you guess why I am asking you to include country of residence as a predictor, and if so, what kind of modelling strategy is being suggested to you here?
Potentially this will help to better understand the effect of different countries. Some countries might have a historically higher religiousness, and it is important to control for that. Also, There might be some patterns within a country and then we shall go and dive deeper and explore the relations within each country.

